Kanwal (2017) BDA Notebook

### 2018-03-31 kanwal-analysis/BDA-analysis.Rmd
added baseline mode comparison. baseline simply chooses the optimal strategy in all of the contidions (ignoring "neither" condition).

x1 <- '115.98.55.114'
x2 <- '117.217.210.9'
# but worked on second time
dfAll2 <- dfAll %>% filter(IP != x2,
                           condition !='neither')
```

Note: slow running.
```{r run-bda-model}
# pt <- proc.time()
# df_bda <- rwebppl::webppl(model_bda, data=dfModelable, data_var='rData')
# et <- proc.time() - pt
# write.csv(df_bda, "bda-tuned-params-20180303.csv")
```

@@

>>>>

problemIPs <- c('70.198.5.150', 
                '117.217.210.9', 
                '65.183.140.246', 
                '24.253.233.194', 
                '24.20.229.200', 
                '108.196.136.202',
                '122.161.26.31')
# 24.74.13.244 only after 10000 attempts
# 50.153.162.232
# 
# but worked on second time
dfAll2 <- dfAll %>% filter(!(IP %in% problemIPs))
```

Note: slow running.
```{r run-bda-model}
# pt <- proc.time()
# df_bda <- rwebppl::webppl(model_bda, data=dfAll2, data_var='rData')
# et <- proc.time() - pt
# write.csv(df_bda, "bda-tuned-params-20180303.csv")
```

@@

### Baseline comparison  - naive model

The naive model employs the optimal strategy for communication in each of the three conditions.
* `combined`: always use `short` form for frequent object, always use `long` form for infrequent object
* `accuracy`: always use `long` form
* `time`: always use `short` form
```{r}
dfEmpSynthAdd <- dfEmpSynth %>%
  filter(data_type=='empirical') %>%
  mutate(baseline=ifelse((condition=='combined' & display_type=='frequent') | 
                               (condition=='accuracy' & display_type=='infrequent') |
                               (condition=='time'), 1.0, 0.0)) %>%
  select(IP, condition, display_type, baseline) %>%
  rename(prop=baseline) %>%
  mutate(data_type='baseline')

dfEmpSynthBaseline <- rbind(dfEmpSynth, dfEmpSynthAdd)
```

```{r plot-model-comparison-data}
dfEmpSynthBaseline %>%
  filter(condition != 'neither') %>%
  spread(display_type, prop) %>%
  ggplot() +
    geom_jitter(aes(x=frequent, y=infrequent, col=condition), alpha=0.5, width=0.01, height=0.01, size=2) +
    ggtitle("Model vs Empirical predictions Kanwal (2017)") +
    theme_few() +
    theme(plot.title = element_text(hjust = 0.5)) +
    facet_grid(~data_type)
```

```{r plot-model-comparison-corr}
dfEmpSynthBaseline %>%
  filter(condition != 'neither') %>%
  spread(data_type, prop) %>%
  gather(model, prop, c(baseline, synthetic)) %>%
  ggplot(aes(x=prop, y=empirical)) +
    geom_point(alpha=0.5, size=2) +
    geom_smooth(method='lm') +
    ggtitle("Model vs Empirical predictions Kanwal (2017)") +
    theme_few() +
    theme(plot.title = element_text(hjust = 0.5)) +
    facet_grid(~model)
```

```{r correlation-baseline}
dfBaselineCor <- dfEmpSynthBaseline %>%
  filter(condition != 'neither') %>%
  spread(data_type, prop)

cor(dfBaselineCor$baseline,
    dfBaselineCor$empirical)^2

```
